Designing Robust Controllers With Optimal $H_{\infty}$ Performance Using Frequency-Domain Data

### 2017-02-27 Papers/Nonlinear Optimization/Latex/Draft/Draft.tex
updated files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, a new frequency-domain method for designing robust controllers is proposed that provides optimal $\mathcal{H}_{\infty}$ performance. A nonlinear optimization problem is formulated which guarantees the stability of the closed-loop system whilst ensuring robust performance. It is shown that the optimal solution to the $\mathcal{H}_\infty$ problem is attained for a fixed-structure controller without any conservatism. A convexified version of the $\mathcal{H}_{\infty}$ criterion has been established in many works and have utilized a similar frequency gridding process; therefore, it is of interest to determine the definiteness of the solution produced by this convex optimization method with respect to the solution of the optimal $\mathcal{H}_{\infty}$ problem proposed in this work. 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
The uncertainties associated with many of today's complex systems pose challenging tasks for engineers and researchers within the control systems community. These uncertainties can cause performance degradations and stability problems that may lead to catastrophic events. Robust controller design methods seek to rectify this issue by designing controllers that ensure proper stability margins whilst maintaining suitable performance.

The robust controller design methodology can be realized in two manners: using time-domain or frequency-domain data. In this paper, the frequency-domain approach will be utilized for the controller design scheme. In a data-driven setting, this frequency domain approach can be used to avoid unmodeled dynamics associated with parametric models. A survey on the differences associated with model-based control and data-driven control has been addressed in \cite{HW13} and \cite{BCE12}. The authors in \cite{HDAV10} use the frequency response data of a stable system to design an optimal controller through a symmetric root locus technique. A robust frequency-domain control design method has been established in \cite{KNND13b} that requires a solution to a non-linear optimization problem. A frequency-domain loop-shaping approach to design fixed-structure controllers is presented in \cite{KNND13c}. However, in this method, the closed-loop stability is not guaranteed and should be verified a posteriori.

Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. Solving the $\mathcal{H}_{\infty}$ problem can be accomplished in a variety of manners. A convex approximation of the $\mathcal{H}_\infty$ criterion has been discussed in \cite{KG10} and \cite{KGL08} where convex constraints are imposed on the Nyquist diagram. The problem is convexified by constructing a linearly parameterized controller and devising linear constraints with respect to a desired open-loop transfer function.  A frequency-domain approach for computing low-order multivariable linearly parameterized controllers is presented in \cite{SOW10}. The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller. An iterative algorithm is used that converges to a local optimal solution of the non-convex problem. However, in \cite{HAB13},  a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraint is used which is based on an initial stabilizing controller. The extension of this method to design multivariable PID controllers for stable systems is presented in \cite{BHA16}. This method uses the same convex approximation as in  \cite{SOW10} but is limited to stable systems and PID structure. More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{UYY16} and \cite{KK16}. These methods use the concepts from \cite{BHA16} to linearize non-convex constraints around an operating point.

In some of the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, these approximations do not yield the true global optimal solution to the $\mathcal{H}_{\infty}$ problem. This paper presents an extension of the work in \cite{KNZ16}, and its purpose is to devise a new frequency-domain approach for obtaining the optimal solution to the $\mathcal{H}_{\infty}$ problem. In \cite{KNZ16}, it was shown that the optimal solution is obtained when the order of the controller increases to infinity; in the proposed method, the optimal solution can be obtained for a fixed low-order fully-parameterized controller (which has desirable practical implications). A nonlinear optimization problem is formulated to guarantee stability of the closed-loop system while ensuring robust performance (without any approximation). Additionally, it will be shown that the proposed method produces a solution that converges to the global optimal solution of the $\mathcal{H}_{\infty}$ problem under certain conditions. A preset frequency grid will be used to satisfy the robust performance condition and solve for a finite number of constraints. It is desired to compare the solutions produced from the convex optimization algorithms in \cite{KNZ16} with the proposed algorithm and correlate the results.

@@

\subsection{Class of Controllers}
The controllers $X(s)$ and $Y(s)$ for this control scheme will be parameterized in the decision vector $\bm{\rho}$, and can be expressed as
\begin{equation}
\begin{aligned} \label{eq:cont}
X(\bm{\rho},s) &= \bm{\rho}_x^{\top} \bm{\phi}_x(\bm{\rho},s)\\
Y(\bm{\rho},s) &= \bm{\rho}_y^{\top} \bm{\phi}_y(\bm{\rho},s)\\
\end{aligned}
\end{equation}
where $\bm{\rho}_x \in \mathbb{R}^{n_x}$, $\bm{\rho}_y \in \mathbb{R}^{n_y}$, and $\{\bm{\phi}_x(\bm{\rho},s), \bm{\phi}_y(\bm{\rho},s)\}$ are vectors of stable transfer functions chosen from a set of orthogonal basis functions. An example of such a function is the Laguerre basis function \cite{Kar13}:
\begin{equation} \label{eq:Laguerre}
\phi_{\{x,y\}_1}(s)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},s) = \frac{\sqrt{2 \rho_c}(s-\rho_c)^{q-2}}{(s+\rho_c)^{q-1}}
\end{equation}
for $q = 2,\ldots,\{n_x,n_y\}$, where $\rho_c \in \mathbb{R}_+$. For discrete-time systems, the Laguerre basis function can be expressed as follows:
\begin{equation} \label{eq:Laguerre_z}
\phi_{\{x,y\}_1}(z)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},z) = \frac{\rho_d^*(1-\rho_d z)^{q-2}}{(z-\rho_d)^{q-1}}
\end{equation}
where $\rho_d^* = \sqrt{1-\rho_d^2}$ and $\{\rho_d \in \mathbb{R}: -1 < \rho_d < 1\}$. Note that when $\rho_d = 0$, the discrete-time Laguerre basis function becomes a simple finite-impulse response (FIR) filter.

A PID controller can also be represented in coprime form. Suppose that the desired controller structure is given as:
\begin{equation} \label{eq:pid}
K(\bm{\rho},s)=\rho_1 + \rho_2 \frac{1}{s} + \rho_3 \frac{s}{T_fs+1}
\end{equation}
Then the coprime controllers can be expressed as follows:
\begin{equation}
\begin{aligned} \label{eq:pid_2}
X(\bm{\rho},s) &= \frac{(\rho_1 T_f+\rho_3)s^2 + (\rho_1+\rho_2 T_f)s + \rho_2}{(s+\rho_c^{\prime})^2}\\
Y(\bm{\rho},s) &= \frac{s(T_fs+1)}{(s+\rho_c^{\prime})^2}
\end{aligned}
\end{equation}
where $\rho_c^{\prime} \in \mathbb{R}_+$. With the PID, note that if $\rho_c^{\prime}$ is fixed, then the coprime $X$ is linearly parameterized while $Y$ is a TF independent of the decision variables. This will always be the case when the controller $K$ is linearly parameterized.
\section{Problem Formulation} \label{sec:problem_form}
The methods described in this paper are associated with minimizing the $\mathcal{H}_{\infty}$ norm of a desired weighted sensitivity function. The sensitivity function $S(s)$ and complementary sensitivity function $T(s)$ associated with this control scheme can be formulated as follows:
\begin{equation}
\begin{aligned} \label{eq:S}
S(s) &:= e/r =[1+L(\bm{\rho},s)]^{-1} \\ &=  M(s)Y(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned} \label{eq:T}
T(s) &:= y/r =L(\bm{\rho},s)[1+L(\bm{\rho},s)]^{-1} \\ &=  N(s)X(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
where $L(\bm{\rho},s) = G(s)K(\bm{\rho},s)$; $r$ is the reference input; $y$ is the system output; $e$ is the tracking error signal (i.e., $e = r-y$). From the above definitions of the sensitivity functions, it can be observed that $S(s)+T(s)=1$.

@@

\subsection{Optimal $\mathcal{H}_{\infty}$ Performance}
In \cite{KNZ16}, it is shown that when the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ approach infinity, then $\gamma$ from (\ref{eq:convex_con}) approaches the optimal solution to the $\mathcal{H}_{\infty}$ problem. However, it is impractical and sometimes impossible to implement large order controllers in a real system.

One solution to this problem is to find the optimal solution for a fixed low-order controller. According to Lemma \ref{lem1}, it is known that there exists a stable transfer function $F$ such that the constraint to the $\mathcal{H}_{\infty}$ problem is satisfied. Therefore, the optimal solution to this problem can be accomplished by fixing the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ and implementing the following optimization problem:
\begin{equation} \label{eq:opt_true}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |F(\bm{\rho})|\big[  |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \big] \\ &&& \hspace{3.3cm}<   \Re\{F(\bm{\rho})\psi(\bm{\rho}) \}  \\ 
& & & \forall \omega \in \Omega \quad 
\end{aligned}
\end{equation}
where $F(\bm{\rho})$ can be chosen such that it incorporates the Laguerre basis functions defined in (\ref{eq:Laguerre}), i.e.,
\begin{equation} \label{eq:Laguerre_sum_c}
F(\bm{\rho}) = \rho_{f_{1}}+ \sum_{p=2}^{q} \rho_{f_{p}}\frac{\sqrt{2 \rho_o}(s-\rho_o)^{p-2}}{(s+\rho_o)^{p-1}}
\end{equation}
where $\rho_o \in \mathbb{R}_+$. It should be noted that the optimal solution to the $\mathcal{H}_\infty$ problem is achieved when $K(\bm{\rho}) = X(\bm{\rho})Y^{-1}(\bm{\rho})$ has the same structure as the optimal controller. However, if the structure of the optimal controller is unknown a priori, then one can simply fix the order of the basis $F(\bm{\rho})$ and vary the orders of the controllers $X(\bm{\rho})$ and $Y(\bm{\rho})$ until $\gamma$ converges to a constant value. The concept of this method will be shown in one of the examples in section \ref{sec:sim}.

It will now be shown that the solution to the optimization problem in (\ref{eq:opt_true}) converges monotonically to the optimal solution of the $\mathcal{H}_\infty$ problem as the order of $F(\bm{\rho})$ increases. The proof will omit the dependence on $\bm{\rho}$ since the result is independent on the parameterization of the basis functions.

@@

Note that the constraint in the optimization problem (\ref{eq:opt_true}) is not convex and a non-linear optimization algorithm will need to be implemented in order to solve this problem. In this manner, the parameter $\rho_o$ in $F(\bm{\rho})$ need not be fixed, and the optimal solution can be obtained for a lower-order $F(\bm{\rho})$ (as will be demonstrated in subsequent sections of this paper).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, a new data-driven method for designing robust controllers is proposed that provides $\mathcal{H}_{\infty}$ performance. A nonlinear optimization problem is formulated which optimizes the parameters of the fixed-structure controller basis function and guarantees the stability of the closed-loop system whilst ensuring robust performance. It is shown that by optimizing the controller basis function parameters, the $\mathcal{H}_\infty$ performance can be significantly improved (without any conservatism). A convexified version of the $\mathcal{H}_{\infty}$ criterion has been established in many works and have utilized a similar frequency gridding process; therefore, it is of interest to determine the definiteness of the solution produced by this convex optimization method with respect to the solution of the $\mathcal{H}_{\infty}$ formulation proposed in this work. The simulation examples illustrate how the proposed method can be used to eliminate the sensitivity associated with the controller basis function parameters and optimize the system performance.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Due to the significant technological advances in the control systems industry, controller design schemes for practical applications are becoming less trivial. In order to simplify the design process, systems are approximated with low-order models in order to reduce the complexity of the design strategy. However, this approximation can lead to stability and performance degradations since these low-order models are subject to model uncertainty. The data-driven control strategy mitigates the problems associated with the model based controller design since the data-driven scheme avoids the problem of unmodeled dynamics associated with low-order parameteric models. A survey on the differences between the model-based control and data-driven control schemes has been addressed in \cite{HW13} and \cite{FK13a}. The data-driven controller design methodology can be realized in two manners: using time-domain or frequency-domain data. In this paper, the frequency-domain approach will be utilized for the controller design scheme. It is important to note that the term ``data-driven"  in this paper signifies that the controller synthesis is independent of the parametric model of the process. In other words, controllers are synthesized by only using the frequency response of the process.

%The authors in \cite{HDAV10} use the frequency response data of a stable system to design an optimal controller through a symmetric root locus technique. A robust frequency-domain control design method has been established in \cite{KNND13b} that requires a solution to a non-linear optimization problem. A frequency-domain loop-shaping approach to design fixed-structure controllers is presented in \cite{KNND13c}. However, in this method, the closed-loop stability is not guaranteed and should be verified a posteriori.

Robust controller design methods belonging to the $\mathcal{H}_{\infty}$ control framework minimizes the $\mathcal{H}_{\infty}$ norm of a weighted closed-loop sensitivity function. This minimization is usually accomplished by formulating an optimization problem; the main concern in solving this optimization problem is convexity and ensuring closed-loop stability. Solving the $\mathcal{H}_{\infty}$ problem can be accomplished in a variety of manners. For fixed-structure controllers, many works use linearly parameterized (LP) controllers in order to convexify the $\mathcal{H}_{\infty}$ problem and ensure that a global solution is obtained. A convex approximation of the $\mathcal{H}_\infty$ criterion has been discussed in \cite{KG10} and \cite{KGL08} where convex constraints are imposed on the Nyquist diagram. The problem is convexified by constructing a LP controller and devising linear constraints with respect to a desired open-loop transfer function.  A frequency-domain approach for computing low-order multivariable LP controllers is presented in \cite{SOW10}. The $\mathcal{H}_{\infty}$ constraints are convexified around an initial stabilizing controller. An iterative algorithm is used that converges to a local optimal solution of the non-convex problem. However, in \cite{HAB13},  a convex-concave approximation of the $\mathcal{H}_{\infty}$ constraint is used which is based on an initial stabilizing controller. The extension of this method to design multivariable PID controllers for stable systems is presented in \cite{BHA16}. This method uses the same convex approximation as in \cite{SOW10} but is limited to stable systems and PID structure. More recent works that implement an iterative loop-shaping method that ensures $\mathcal{H}_{\infty}$ performance have been devised in \cite{UYY16} and \cite{KK16}. These methods use the concepts from \cite{BHA16} to linearize non-convex constraints around an operating point and implement LP controllers to ensure convexity.

In some of the works asserted above, it has been proved that a convex approximation of the $\mathcal{H}_{\infty}$ problem yields favorable results; however, the linear parameterization process limits the performance of these control systems since it is unknown a priori which controller basis function optimizes the performance. For certain applications, the selection of the fixed-structure basis function can be sensitive to both the order and the free parameters of the basis function (such as the Laguerre parameter in the basis function presented in \cite{KNZ16}). This paper presents an extension of the work in \cite{KNZ16}, and its purpose is to devise a new data-driven approach for improving the performance associated with the $\mathcal{H}_{\infty}$ problem. In \cite{KNZ16}, it was shown that by solving a convex optimization problem, the optimal solution is obtained when the order of the controller increases to infinity. In the proposed method, the solution can be improved for a fixed structure low-order fully-parameterized controller (which has desirable practical implications) by formulating non LP controllers where the basis function parameters are optimized. A nonlinear optimization problem is formulated to guarantee stability of the closed-loop system while ensuring robust performance (without any approximation). A preset frequency grid will be used to satisfy the robust performance condition and solve for a finite number of constraints. It is desired to compare the solutions produced from the convex optimization algorithms in \cite{KNZ16} with the proposed algorithm and correlate the results.

@@

\subsection{Class of Controllers}
The controllers $X(s)$ and $Y(s)$ for this control scheme will be parameterized in the decision vector $\bm{\rho}$, and can be expressed as
\begin{equation}
\begin{aligned} \label{eq:cont}
X(\bm{\rho},s) &= \bm{\rho}_x^{\top} \bm{\phi}_x(\bm{\rho},s)\\
Y(\bm{\rho},s) &= \bm{\rho}_y^{\top} \bm{\phi}_y(\bm{\rho},s)\\
\end{aligned}
\end{equation}
where $\bm{\rho}_x \in \mathbb{R}^{n_x}$, $\bm{\rho}_y \in \mathbb{R}^{n_y}$, and $\{\bm{\phi}_x(\bm{\rho},s), \bm{\phi}_y(\bm{\rho},s)\}$ are vectors of stable transfer functions chosen from a set of orthogonal basis functions. An example of such a function is the Laguerre basis function \cite{Kar13}:
\begin{equation} \label{eq:Laguerre}
\phi_{\{x,y\}_1}(s)=1,\ \phi_{\{x,y\}_q}(\bm{\rho},s) = \frac{\sqrt{2 \rho_{\{x,y \}}^c}\left(s-\rho_{\{x,y \}}^c\right)^{q-2}}{\left(s+\rho_{\{x,y \}}^c\right)^{q-1}}
\end{equation}
for $q = 2,\ldots,\{n_x,n_y\}$, where $\rho_{\{x,y \}}^c \in \mathbb{R}_+$. The subscript $\{x,y \}$ is used to represent the basis function for the controller $X(\bm{\rho},s) $ or $Y(\bm{\rho},s) $. For discrete-time systems, the Laguerre basis function can be expressed as follows:
\begin{equation} \label{eq:Laguerre_z}
\phi_{\{x,y\}_1}(z)=1,\quad \phi_{\{x,y\}_q}(\bm{\rho},z) = \frac{\rho_{\{x,y \}}^*\left(1-\rho_{\{x,y \}}^d z\right)^{q-2}}{\left(z-\rho_{\{x,y \}}^d\right)^{q-1}}
\end{equation}
where $\rho_{\{x,y \}}^* = \sqrt{1-(\rho_{\{x,y \}}^d)^2}$ and $$\{\rho_{\{x,y \}}^d \in \mathbb{R}: -1 < \rho_{\{x,y \}}^d < 1\}$$ Note that when $\rho_{\{x,y \}}^d = 0$, the discrete-time Laguerre basis function becomes a simple finite-impulse response (FIR) filter.

A PID controller can also be represented in coprime form. Suppose that the desired controller structure is given as:
\begin{equation} \label{eq:pid}
K(\bm{\rho},s)=\rho_1 + \rho_2 \frac{1}{s} + \rho_3 \frac{s}{T_fs+1}
\end{equation}
Then the coprime controllers can be expressed as follows:
\begin{equation}
\begin{aligned} \label{eq:pid_2}
X(\bm{\rho},s) &= \frac{(\rho_1 T_f+\rho_3)s^2 + (\rho_1+\rho_2 T_f)s + \rho_2}{(s+\rho_c^{\prime})^2}\\
Y(\bm{\rho},s) &= \frac{s(T_fs+1)}{(s+\rho_c^{\prime})^2}
\end{aligned}
\end{equation}
where $\rho_c^{\prime} \in \mathbb{R}_+$. With the PID, note that if $\rho_c^{\prime}$ is fixed, then the coprime $X$ is linearly parameterized while $Y$ is a TF independent of the decision variables. This will always be the case when the controller $K$ is linearly parameterized.
\section{Problem Formulation} \label{sec:problem_form}
The methods described in this paper are associated with minimizing the $\mathcal{H}_{\infty}$ norm of a desired weighted sensitivity function. The sensitivity function $S(s)$ and complementary sensitivity function $T(s)$ associated with this control scheme can be formulated as follows:
\begin{equation}
\begin{aligned} \label{eq:S}
S(s) &:= e(s)/r(s) =[1+L(\bm{\rho},s)]^{-1} \\ &=  M(s)Y(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned} \label{eq:T}
T(s) &:= y(s)/r(s) =L(\bm{\rho},s)[1+L(\bm{\rho},s)]^{-1} \\ &=  N(s)X(\bm{\rho},s)[N(s)X(\bm{\rho},s)+M(s)Y(\bm{\rho},s)]^{-1}\\
\end{aligned}
\end{equation}
where $L(\bm{\rho},s) = G(s)K(\bm{\rho},s)$; $r(s)$ is the frequency function of the reference input; $y(s)$ is the frequency function of the system output; $e(s)$ is the frequency function of the tracking error signal (i.e., $e(s) = r(s)-y(s)$). From the above definitions of the sensitivity functions, it can be observed that $S(s)+T(s)=1$.

@@

\subsection{Optimal $\mathcal{H}_{\infty}$ Performance}
In order to preserve the convexity of the $\mathcal{H}_{\infty}$ problem (with fixed-structure controllers), it is necessary to invoke linearly parameterized controllers that contain basis functions with fixed values (as asserted by the various works mentioned in the Introduction). For example, the problem in (\ref{eq:convex_con}) is convex only if $X(\bm{\rho})$ and $Y(\bm{\rho})$ are linearly parameterized. Therefore, the value of $\rho_c$ in the Laguerre basis functions (\ref{eq:Laguerre}) must be fixed a priori. The solution to the convex problem guarantees a global solution; however, the solution may not be the optimal global solution to the \textit{convex problem} since the the Laguerre parameter is not optimized.

In \cite{KNZ16}, it is shown that when the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ approach infinity, then $\gamma$ from (\ref{eq:convex_con}) approaches the optimal solution to the $\mathcal{H}_{\infty}$ problem. However, it is impractical and sometimes impossible to implement large order controllers in a real system.

One solution to this problem is to find the optimal solution for a fixed low-order controller. According to Lemma \ref{lem1}, it is known that there exists a stable transfer function $F$ such that the constraint to the $\mathcal{H}_{\infty}$ problem is satisfied. Therefore, the optimal solution to this problem can be accomplished by fixing the orders of $X(\bm{\rho})$ and $Y(\bm{\rho})$ and implementing the following optimization problem:
\begin{equation} \label{eq:opt_true}
\begin{aligned}
& \underset{ \bm{\rho}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \gamma^{-1} |F(\bm{\rho})|\big[  |W_1MY(\bm{\rho})| + |W_2 NX(\bm{\rho})| \big] \\ &&& \hspace{3.3cm}<   \Re\{F(\bm{\rho})\psi(\bm{\rho}) \}  \\ 
& & & \forall \omega \in \Omega \quad 
\end{aligned}
\end{equation}
Note that $F(\bm{\rho}) $ must be a stable basis function (as asserted in Lemma.\ref{lem1}) in order to ensure that the closed-loop system is stable. Therefore, $F(\bm{\rho})$ can be chosen such that it incorporates the Laguerre basis functions defined in (\ref{eq:Laguerre}), i.e.,
\begin{equation} \label{eq:Laguerre_sum_c}
F(\bm{\rho}) = \rho_{f_{1}}+ \sum_{p=2}^{q} \rho_{f_{p}}\frac{\sqrt{2 \rho_o}(s-\rho_o)^{p-2}}{(s+\rho_o)^{p-1}}
\end{equation}
where $\rho_o \in \mathbb{R}_+$. A similar representation can be made for discrete-time systems (i.e., using the Laguerre basis functions in (\ref{eq:Laguerre_z})).

\iffalse
It will now be shown that the solution to the optimization problem in (\ref{eq:opt_true}) converges monotonically to the optimal solution of the $\mathcal{H}_\infty$ problem as the order of $F(\bm{\rho})$ increases. The proof will omit the dependence on $\bm{\rho}$ since the result is independent on the parameterization of the basis functions.

@@

\fi
Note that the constraint in the optimization problem (\ref{eq:opt_true}) is not convex and a non-linear optimization algorithm will need to be implemented in order to solve this problem. In this manner, the parameter $\rho_o$ in $F(\bm{\rho})$ need not be fixed, and the optimal solution can be obtained for a lower-order $F(\bm{\rho})$ (as will be demonstrated in subsequent sections of this paper).
